Numerical trajectory patterns of floating macroalgae

### 2021-03-15 thesis_chapter_3.Rmd
study site updated

The region of interest for this study was the Cape Peninsula in the Western Cape (Figure 1A). A release site was chosen for this study, Kommetjie, which is located on the Atlantic side of the Cape Peninsula (Figure 2B). The hydrodynamics in the study region are driven by a complex interaction of wind and waves, which are also influenced by larger oceanic processes. In South Africa, the larger processes can largely be attributed to the Agulhas Current (AC) and the Benguela Current (BC)[@lutjeharms2000;@lutjeharms2007;@garzoli1996;@Hutchings2009;@rubio2009]. The AC is a component of the South-west Indian Ocean sub-gyre, flowing predominantly south-westward following the continental shelf edge and eventually retroflecting eastward back into the South Indian Ocean [@@lutjeharms2000;@lutjeharms2007]. The region where the retroflection occurs is known as the Agulhas retroflection and consists of high levels of mesoscale variability [@garzoli1996]. The variability results in shedding of rings and filaments known as the Agulhas Rings and have an average diameter of ~324km [@lutjeharms1988; @lutjeharms2006; @lutjeharms2007]. The Agulhas Rings are the main contributors to the Agulhas leakage which are the transport of warm water from the Indian Ocean to the South Atlantic Ocean [@garzoli1996; @lutjeharms2006; @beal2015]. The Agulhas leakage is also a source of meso-scale variability within the Benguela region as anticyclonic rings are shed and drift northwestward along the southern Benguela slope region [@rubio2009]. The Benguela region is characterised by strong coastal upwelling cells which are primarily driven by equatorward winds [@shannon1996; @hardman2003], and is known as the Benguela upwelling region. The Benguela upwelling region starts at 27$^\circ$S and extends southward to 35$^\circ$S [@shannon1996]. The region is also characterised by high amounts of mesoscale variability in the form of eddies and filaments [@blanke2002; @blanke2005; @rubio2009]. The Benguela inshore region is dominated by a northwestward flow as a result of topographical steering, wind stress and interactions with passing Agulhas rings and eddies [@veitch2010].

>>>>

The region of interest for this study was the Cape Peninsula in the Western Cape (Figure 1A). A release site was chosen for this study, Kommetjie, which is located on the Atlantic side of the Cape Peninsula (Figure 2B). The hydrodynamics in the study region are driven by a complex interaction of wind and waves, which are also influenced by larger oceanic processes. In South Africa, the larger processes can be attributed to the Agulhas Current (AC) and the Benguela Current (BC)[@lutjeharms2000;@lutjeharms2007;@garzoli1996;@Hutchings2009;@rubio2009]. The AC is a component of the South-west Indian Ocean sub-gyre, flowing predominantly south-westward following the continental shelf edge and eventually retroflecting eastward back into the South Indian Ocean [@lutjeharms2000;@lutjeharms2007]. The region where the retroflection occurs is known as the Agulhas Retroflection and consists of high levels of mesoscale variability [@garzoli1996]. The variability results in shedding of rings and filaments known as the Agulhas Rings and have an average diameter of ~324km [@lutjeharms1988; @lutjeharms2006; @lutjeharms2007]. The Agulhas Rings are the main contributors to the Agulhas leakage which are the transport of warm water from the Indian Ocean to the South Atlantic Ocean [@garzoli1996; @lutjeharms2006; @beal2015]. The Agulhas leakage is also a source of meso-scale variability within the Benguela region as anticyclonic rings are shed and drift northwestward along the southern Benguela slope region [@rubio2009]. The Benguela region is characterised by strong coastal upwelling cells which are primarily driven by equatorward winds [@shannon1996; @hardman2003]. It is known as the Benguela Upwelling System (BUS) The BUS starts at 27$^\circ$S and extends southward to 35$^\circ$S [@shannon1996]. The region is also characterised by high amounts of mesoscale variability in the form of eddies and filaments [@blanke2002; @blanke2005; @rubio2009]. The Benguela inshore region is dominated by a northwestward flow because of topographical steering, wind stress and interactions with passing Agulhas Rings and eddies [@veitch2010].
